\documentclass{article}
\author{Mathias Bertelsen}
\title{SVN guide}
\usepackage{hyperref}
\usepackage{multicol}

\begin{document}

\maketitle

\tableofcontents
\newpage

\section{Guide}

\subsection{Roles}
\label{subsec:roles}

\textbf{Team Leader:}
\begin{itemize}
	\item Mathias Bertelsen
\end{itemize} \medskip

\noindent \textbf{CSS:}
\begin{itemize}
	\item Edoardo Riggio
	\item Hoormazd Pirayeshfar
\end{itemize} \medskip

\noindent \textbf{SVN:}
\begin{itemize}
	\item Matteo Bernaschina
\end{itemize} \medskip

\noindent \textbf{Topic Leaders:}
\begin{enumerate}
	\item Bugs: Brian Bronz
	\item Vulnerabilites: Ian Abuaf Pelo
	\item Malicious Code: Matteo Alberici
	\item History: Onciu Razvan Petrica
\end{enumerate} \medskip


\noindent \textbf{Team Members}
\begin{multicols}{2}
\begin{itemize}
\item Alessio Cordivani (bugs)
\item Davide Scannapieco (bugs)
\item Ilker Kaymak (bugs)
\item Kieran Mckee(vulnerabilities)
\item Bahram Ismayilow (vulnerabilities)
\item Michele Cattaneo (malicious code)
\item Kelvin Likollari (malicious code)
\item Claudio Milanesi (history)
\item Marco Mariosa (history)
\item Arianna Bianchi (history)
\item Elena Franchini (history)
\item Massimo Bordogna (history)
\end{itemize} \medskip
\end{multicols}

\noindent \textbf{Optional: Broken Links:}
\begin{itemize}
	\item Michele Cattaneo
\end{itemize} \medskip
\noindent \textbf{Optional: LaTeX:}
\begin{itemize}
	\item Brian Bronz
\end{itemize} \medskip

\newpage
\subsection{Schedule}
\label{subsec:schedule}

\begin{table}[!h]
\centering{
\begin{tabular}{|p{5cm}|l|} \hline
\textbf{What to do} & \textbf{Deadline} \\ \hline
Inception & 28.10.2019 \\
Go / No-Go & 29.10.2019\\
Finish 50\% of content pages & 01.11.2019 \\
Meeting: Team Leader, Topic Leaders, CSS, SVN, Bonus & 01.11.2019 \\
Midway milestone & 04.11.2019 \\
Meeting: Team Leader, Topic Leaders, CSS, SVN, Bonus & 04.11.2019 \\
(Start LaTeX Bonus) & 05.11.2019 \\
Finish draft of webpage &  06.11.2019\\
Meeting: Team Leader, Topic Leaders, CSS, SVN, Bonus & 08.11.2019 \\
Finish corrections  & 09.11.2019 \\
Final milestone & 12.11.2019 \\
Discussion about minor changes to presentation & 17.11.2019 \\
Final presentation & 18.11.2019 \\


\hline
\end{tabular}
\caption{Schedule}
}
\end{table}

\newpage
\subsection{Deadlines}
\label{subsec:deadlines}

\begin{table}[h]
\centering{
\begin{tabular}{|p{4cm}|l|l|} \hline
\textbf{Who} & \textbf{What to do} & \textbf{Deadline} \\ \hline
Team Leader & Add topic\_info.txt to repository & 25.10.2019 \\
SVN & Set up repository & 25.10.2019 \\
Team Leader & Prepare Latex  & 26.10.2019 \\
Topic Leaders & 300 words about content/structure & 26.10.2019 \\
CSS & Add one document to SVN & 26.10.2019 \\
Everyone except Team Leader, CSS, SVN & 300 words about at least one case/topic & 26.10.2019 \\
Everyone & Connect to SVN and add to text file & 26.10.2019 \\
Volunteer & Write guide and send to Team Leader & 26.10.2019 \\
CSS & 200 word and slides about CSS & 27.10.2019 \\
Topic Leaders & Add slides to Presentation & 27.10.2019 \\
Groups & Make 1 overview page and example case & 27.10.2019 \\
 & page using CSS style and add it to project & \\
Volunteer & Make draft of index page linking to other & 27.10.2019 \\
 & pages & \\
 Team Leader & Prepare Presentation & 27.10.2019 \\
 Everyone & submit \texttt{.html} file containing ONLY all sources & 08.11.2019 \\
 &  named: \texttt{sources\_initials.html} (see \ref{subsec:bib}) &  \\
 Everyone & Add citations to webpages (see \ref{subsec:cit}) & 09.11.2019 \\
 Team Leader \& CSS & Finish bibliography and citations & 10.11.2019 \\
 Team Leader & Finish LaTeX bonus exercise  & 10.11.2019 \\
 Topics Leaders & 300 word overview of topic  & 13.11.2019 \\
 Topic Leaders & 200 word overview of how working process  & 14.11.2019 \\
 & was (challenges, changes for next time?)& \\
 Team Leader & Finish final presentation slides  & 16.11.2019 \\
 
\hline
\end{tabular}
\caption{Deadlines}
}
\end{table}


\subsection{SVN}
\label{subsubsec:SVN}
To checkout, first use \texttt{cd} to go to your desired working space, and use the following command using Unix Shell: \smallskip

\texttt{svn checkout svn+ssh://your\_user@atelier.inf.usi.ch/home/bernamat/GroupProject/}\smallskip \newline
Then, use the following command inside the GroupProject/ directory to commit: \smallskip

\texttt{svn commit -m "your\_message"}

The working directories for each topic group are located inside the html directory, with the path: \medskip

\texttt{GroupProject/www/html/bugs/}

\texttt{GroupProject/www/html/vulnerabilities/}

\texttt{GroupProject/www/html/malicious\_code/}

\texttt{GroupProject/www/html/history/} \medskip

\noindent You can also just use \texttt {ls} inside the \texttt{html/} directory to find them. \medskip

\noindent The \texttt{GroupProject/guide/} directory will also contain this guide chapter, \texttt{guide.tex} so that all team members can read it.

\subsection{CSS}

The CSS team has prepared a standard CSS template to be used across the whole website which will be available at the following path from the GroupProject directory: \medskip

\texttt{GroupProject/www/stylesheets/main.css} \medskip

\noindent A HTML template will also be available at the following path from the GroupProject directory: \medskip

\texttt{GroupProject/www/html/topic/template.html} \medskip

\noindent A different HTML file can be used if desired, as long as the standard CSS template is used and it complies with both the theme and color palette.

\subsection{Citing and Bibliography}
\label{subsec:bib}

We will be citing and writing the bibliography MLA style. \textbf{Make sure to write down sources as you are working} so you do not have to rediscover all of your sources later on. The structure is as follows: \newline \medskip
\textbf{Books:}
\begin{itemize}
\item Surname, First name. \emph{title}. Publisher, year.
\begin{itemize}
\item Example (one author): Mendelson, Elliott. \emph{3,000 Solved Problems in Calculus.} McGraw-Hill, 2009.
\item Example (multiple authors): Tanenbaum, Andrew S. and Austin, Todd. \emph{Structured Computer Organization.} Pearson, 2013.
\end{itemize}
\end{itemize}

\noindent \textbf{Webpages:}
\begin{itemize} \medskip
\item If author available: 
\begin{itemize}
\item Surname, First name. \emph{title}. Name of webpage, date. URL. Last date accessed.
\item Example : Engle, Jeremy. \emph{Lesson of the Day: ‘Occupy Alcatraz: Native American Activism in the Modern Era’}. The New York Times, 2019. https://www.nytimes.com/2019/10/24/learning/lesson-of-the-day-occupy-alcatraz-native-american-activism-in-the-modern-era.html. Last accessed 25 October 2019.
\end{itemize}
\item Otherwise:
\begin{itemize}
\item Webpage creator name \emph{title}. Name of webpage, date. URL. Last date accessed.
\item Example: EasyBib, \emph{How to Cite A Book in Print in MLA}. EasyBib, 2019. http://www.easybib.com/reference/guide/mla/book. Last accessed 25 October 2019.
\end{itemize}
\end{itemize}

\noindent \textbf{Online Images:}
\begin{itemize} \medskip
\item Surname, First name. \emph{title of image}. Name of webpage, date. URL. Last date accessed.
\item Example : Sanchez, Marcio . \emph{Firefighters worked to douse flames engulfing a home in Santa Clarita, Calif., on Thursday}. The Washington Post, 2019. https://www.washingtonpost.com/weather/2019/10/25/how-powerful-winds-bone-dry-air-are-sparking-wildfire-nightmare-california/. Last accessed 25 October 2019.
\end{itemize}

If you have any problems, such as not being able to find date or author of a webpage, first try an online citation machine, such as this one \href{http://www.citationmachine.net/}{\underline{\emph{Citation Machine}}}
first off write what you believe is appropriate, and then write so in the citation and a Topic Leader or Group Leader will check it later. \medskip

\subsection{Citations on Website:} 
\label{subsec:cit}

On the actual website, you will add citations as superscripted ordered numbers, which will link to the bibliography sections of the website. To give an examples:

\begin{itemize}
\item The final deadline for the project is Tuesday 12 November \textsuperscript{(1)}
\end{itemize}

For now since the order of sources has not been completed superscript \texttt{initials\_number} ordered according to the bibliography you have made. For example I would write:

\begin{itemize}
\item The final deadline for the project is Tuesday 12 November \textsuperscript{(mb\_1)}
\end{itemize}

They will then be ordered after the webpage has been completed, unless another method is suggested before then.



\end{document}
